---
output:  rmarkdown::github_document
---

# SVM Application in R

## use support vector approaches to predict whether a given car gets high or low gas mileage based on the Auto data set.

### author: Yi Rong
### update on 12/30/20

### (1)
Create a binary variable that takes on a 1 for cars with gas mileage above the median, and a 0 for cars with gas mileage below the median.

```{r message=FALSE}
library(ISLR)
library(e1071)
attach(Auto)
## a
mpglevel <- rep(0, nrow(Auto))
mpglevel[Auto$mpg > median(Auto$mpg)] <- 1
Auto$mpglevel <- as.factor(mpglevel)
```

### (2)
Fit a support vector classifier to the data with various values of cost, in order to predict whether a car gets high or low gas mileage. Determine the best value of this parameter using the cross-validation errors associated with different values of this parameter.

```{r message=FALSE}
## b
set.seed(115)
tune.linear <- tune(svm, mpglevel ~ ., data = Auto, kernel = "linear", 
                 ranges = list(cost = c(0.001, 0.01, 0.1, 1, 5, 10, 100)))
summary(tune.linear)
# The least error appears when cost is 1.
```


### (3)
Use SVMs with radial and polynomial basis kernels, with different values of gamma and degree and cost. Determine the best values of these parameters.

```{r message=FALSE}
## c
# poly
set.seed(116)
tune.poly <- tune(svm, mpglevel ~ ., data = Auto, kernel = "polynomial", 
                 ranges = list(cost = c(0.001, 0.01, 0.1, 1, 5, 10, 100), 
                               degree = c(2, 3, 4)))
summary(tune.poly)
# The least error appears when cost is 100 and degree is 2.

# radial
set.seed(117)
tune.radial <- tune(svm, mpglevel ~ ., data = Auto, kernel = "radial", 
                 ranges = list(cost = c(0.001, 0.01, 0.1, 1, 5, 10, 100), 
                               gamma = c(0.001, 0.01, 0.1, 1, 5, 10, 100)))
summary(tune.radial)
# The least error appears when cost is 100 and gamma is 0.01.

best.linear <- svm(mpglevel ~ ., data = Auto, kernel = "linear", cost = 1)
best.poly <- svm(mpglevel ~ ., data = Auto, kernel = "polynomial", cost = 100, degree = 2)
best.radial <- svm(mpglevel ~ ., data = Auto, kernel = "radial", cost = 100, gamma = 0.01)
```

### (4)
Make some plots to visualize SVMs created in (b) and (c).

```{r message=FALSE}

names.Auto <- names(Auto)[-c(1, 9, 10)]
for (name in names.Auto) {
  par(col.main='white')
  plot(best.linear, Auto, as.formula(paste("mpg~", name, sep = "")), main="")
  par(col.main='black')
  title("Linear SVM")
  }
for (name in names.Auto) {
  par(col.main='white')
  plot(best.poly, Auto, as.formula(paste("mpg~", name, sep = "")), main="")
  par(col.main='black')
  title("Poly SVM")
}
for (name in names.Auto) {
  par(col.main='white')
  plot(best.radial, Auto, as.formula(paste("mpg~", name, sep = "")), main="")
  par(col.main='black')
  title("Radial SVM")
}
```

